Distributed Range-Only Localisation that Preserves Sensor and Navigator Privacies

### 2021-06-10 main.tex
Fixed error in equations where measurement vector and matrix were treated as 2 dimensional rather than 4. Small notation change has bene made to make the pseudocode handle this change accordingly

% Graphics
\usepackage{tikz}
\usepackage{graphicx}
% Maths
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amsthm}
\usepackage{mathtools}
% Algorithms
\usepackage{algorithm}
\usepackage{algpseudocode}
% Local
\usepackage{ISASmacros/isasmathmacros}
% Equal last columns
\usepackage{flushend}

@@

@@

                &(2r_{k,i}^{\prime-1})\hat{x}_{k|k-1}^3 + (2r_{k,i}^{\prime-1})\hat{x}_{k|k-1}\hat{y}_{k|k-1}^2 \\

@@

                &\quad+ (2r_{k,i}^{\prime-1}s_{x,i}s_{y,i}^2) + (-2r_{k,i}^{\prime-1}s_{x,i} z'_{k,i})
            \vspace{5pt}\\

@@

                &(2r_{k,i}^{\prime-1})\hat{y}_{k|k-1}^3 + (2r_{k,i}^{\prime-1})\hat{x}_{k|k-1}^2\hat{y}_{k|k-1} \\

@@

                &\quad+ (2r_{k,i}^{\prime-1}s_{y,i}^3) + (-2r_{k,i}^{\prime-1}s_{y,i}z'_{k,i})

@@

        \end{bmatrix}

@@

            \beta_{11} & \beta_{12} \\
            \beta_{21} & \beta_{22}

@@

    \beta_{11} &= (4r_{k,i}^{\prime-1})\hat{x}_{k|k-1}^2 + (-8r_{k,i}^{\prime-1}s_{x,i})\hat{x}_{k|k-1} + (4r_{k,i}^{\prime-1}s_{x,i}^2)\,, \\

@@

        \beta_{12} &= (4r_{k,i}^{\prime-1})\hat{x}_{k|k-1}\hat{y}_{k|k-1} + (-4r_{k,i}^{\prime-1}s_{y,i})\hat{x}_{k|k-1}  \\

@@

    \beta_{21} &= \beta_{12}\,,\ \textrm{and} \\
    \beta_{22} &= (4r_{k,i}^{\prime-1})\hat{y}_{k|k-1}^2 + (-8r_{k,i}^{\prime-1}s_{y,i})\hat{y}_{k|k-1} + (4r_{k,i}^{\prime-1}s_{y,i}^2)\,.

@@

    \State Let $\alpha_{v}^{(i)}$ represent an encryption of element $v$ in $\vec{i}'_{k,i}$ from \eqref{eqn:hrz_linear_comb}
    \State $\alpha_{1}^{(i)} \gets \mathcal{E}_{pk_0}(\mathsf{E}_{0}(\hat{x}^3_{k|k-1}))^{\mathsf{E}_{0}(2r_{k,i}^{\prime-1})}\cdot$\par
    \ $\mathcal{E}_{pk_0}(\mathsf{E}_{0}(\hat{x}_{k|k-1}\hat{y}^2_{k|k-1}))^{\mathsf{E}_{0}(2r_{k,i}^{\prime-1})}\cdot$\par
    \ $\mathcal{E}_{pk_0}(\mathsf{E}_{0}(\hat{x}^2_{k|k-1}))^{\mathsf{E}_{0}(-r_{k, i}^{\prime-1}s_{x,i})}\cdot$\par
    \ $\mathcal{E}_{pk_0}(\mathsf{E}_{0}(\hat{y}^2_{k|k-1}))^{\mathsf{E}_{0}(-2r_{k, i}^{\prime-1}s_{x,i})}\cdot$\par
    \ $\mathcal{E}_{pk_0}(\mathsf{E}_{0}(\hat{x}_{k|k-1}))^{\mathsf{E}_{0}(2r_{k,i}^{\prime-1}z_{k,i}')}\cdot$\par
    \ $\mathcal{E}_{pk_0}(\mathsf{E}_{0}(\hat{x}_{k|k-1}))^{\mathsf{E}_{0}(-2r_{k,i}^{\prime-1}s_{x,i}^2)}\cdot$\par
    \ $\mathcal{E}_{pk_0}(\mathsf{E}_{0}(\hat{x}_{k|k-1}))^{\mathsf{E}_{0}(-2r_{k,i}^{\prime-1}s_{y,i}^2)}\cdot$\par
    \ $(N+1)^{\mathsf{E}_{1}(2r_{k,i}^{\prime-1}s_{x,i}^3)}
    (N+1)^{\mathsf{E}_{1}(2r_{k,i}^{\prime-1}s_{x,i}s_{y,i}^2)}\cdot$\par
    \ $(N+1)^{\mathsf{E}_{1}(-2r_{k, i}^{\prime-1}s_{x,i}z_{k,i}')}
    H(k\mathbin\|1\mathbin\|1\mathbin\|0)\pmod{N^2}$
    \State Compute $\alpha_{2}^{(i)}$ using \eqref{eqn:hrz_linear_comb}, \eqref{eqn:our_scheme_lin_comb} and the remark from section \ref{sec:lcao_scheme} in the form above
    \For{$v \gets 1$ to $2$}
        \State Send $\alpha_{v}^{(i)}$ to the navigator
    \EndFor

    \State Let $\beta_{vw}^{(i)}$ represent an encryption of element $(v,w)$ in $\mat{I}'_{k,i}$ from \eqref{eqn:hrh_linear_comb}
    \State $\beta_{11}^{(i)} \gets \mathcal{E}_{pk_0}(\mathsf{E}_{0}(\hat{x}^2_{k|k-1}))^{\mathsf{E}_{0}(4r_{k,i}^{\prime-1})}\cdot$\par
    \ $\mathcal{E}_{pk_0}(\mathsf{E}_{0}(\hat{x}_{k|k-1}))^{\mathsf{E}_{0}(-8r_{k, i}^{\prime-1}s_{x,i})}\cdot$\par
    \ $(N+1)^{\mathsf{E}_{1}(4r_{k,i}^{\prime-1}s_{x,i}^2)}\cdot$\par
    \ $H(k\mathbin\|1\mathbin\|1\mathbin\|1)\pmod{N^2}$
    \State Compute remaining $\beta_{vw}^{(i)}$ using \eqref{eqn:hrh_linear_comb}, \eqref{eqn:our_scheme_lin_comb} and the remark from section \ref{sec:lcao_scheme} in the form above
    \For{$v \gets 1$ to $2$}
        \For{$w \gets 1$ to $2$} 
            \State Send $\beta_{vw}^{(i)}$ to the navigator
        \EndFor
    \EndFor
    \EndProcedure
\end{algorithmic}
\end{algorithm}

@@

    \For{$v \gets 1$ to $2$}
        \State Receive $\alpha_{v}^{(i)}$ from each sensor $1\leq i \leq n$
    \EndFor

    \For{$v \gets 1$ to $2$}
        \For{$w \gets 1$ to $2$}
        \State Receive $\beta_{vw}^{(i)}$ from each sensor $1\leq i \leq n$
        \EndFor
    \EndFor

    \State Let $\alpha_{v}$ represent an encryption of element $v$ in $\sum_{i=1}^n\vec{i}'_{k,i}$
    \For{$v \gets 1$ to $2$}
        \State $\alpha_{v} \gets \prod_{i=1}^n\alpha_{v}^{(i)}$
        \State Compute $\mathcal{D}_{sk_0}(\alpha_{v})$ with $\lambda$ by \eqref{eqn:our_scheme_decrypt}
        \State Compute $\mathsf{E}^{-1}_{1}(\mathcal{D}_{sk_0}(\alpha_{v}))$ by \eqref{eqn:decode}
    \EndFor
    \State Construct $\sum_{i=1}^n\vec{i}'_{k,i}$ from decoded decryptions above

    \State Let $\beta_{vw}$ represent an encryption of element $(v,w)$ in $\sum_{i=1}^n\mat{I}'_{k,i}$
    \For{$v \gets 1$ to $2$}
        \For{$w \gets 1$ to $2$}
            \State $\beta_{vw} \gets \prod_{i=1}^n\beta_{vw}^{(i)}$
            \State Compute $\mathcal{D}_{sk_0}(\beta_{vw})$ with $\lambda$ by \eqref{eqn:our_scheme_decrypt}
            \State Compute $\mathsf{E}^{-1}_{1}(\mathcal{D}_{sk_0}(\beta_{vw}))$ by \eqref{eqn:decode}
        \EndFor
    \EndFor
    \State Construct $\sum_{i=1}^n\mat{I}'_{k,i}$ from decoded decryptions above

>>>>

% Graphics
\usepackage{tikz}
\usepackage{graphicx}
% Maths
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amsthm}
\usepackage{mathtools}
\usepackage{bm}
% Algorithms
\usepackage{algorithm}
\usepackage{algpseudocode}
% Local
\usepackage{ISASmacros/isasmathmacros}
% Equal last columns
\usepackage{flushend}

@@

            \alpha_1^{(i)} & 0 & \alpha_2^{(i)} & 0
        \end{bmatrix}^\top\,,

@@

        \alpha_1^{(i)} &= (2r_{k,i}^{\prime-1})\hat{x}_{k|k-1}^3 + (2r_{k,i}^{\prime-1})\hat{x}_{k|k-1}\hat{y}_{k|k-1}^2 \\

@@

        &\quad+ (2r_{k,i}^{\prime-1}s_{x,i}s_{y,i}^2) + (-2r_{k,i}^{\prime-1}s_{x,i} z'_{k,i})\ \textrm{and}

@@

        \alpha_2^{(i)} &= (2r_{k,i}^{\prime-1})\hat{y}_{k|k-1}^3 + (2r_{k,i}^{\prime-1})\hat{x}_{k|k-1}^2\hat{y}_{k|k-1} \\

@@

        &\quad+ (2r_{k,i}^{\prime-1}s_{y,i}^3) + (-2r_{k,i}^{\prime-1}s_{y,i}z'_{k,i})\,,

@@

@@

            \beta_1^{(i)} & 0 & \beta_2^{(i)} & 0 \\
            0 & 0 & 0 & 0 \\
            \beta_3^{(i)} & 0 & \beta_4^{(i)} & 0 \\
            0 & 0 & 0 & 0

@@

    \beta_1^{(i)} &= (4r_{k,i}^{\prime-1})\hat{x}_{k|k-1}^2 + (-8r_{k,i}^{\prime-1}s_{x,i})\hat{x}_{k|k-1} + (4r_{k,i}^{\prime-1}s_{x,i}^2)\,, \\

@@

        \beta_2^{(i)} &= (4r_{k,i}^{\prime-1})\hat{x}_{k|k-1}\hat{y}_{k|k-1} + (-4r_{k,i}^{\prime-1}s_{y,i})\hat{x}_{k|k-1}  \\

@@

    \beta_3^{(i)} &= \beta_{12}\ \textrm{and} \\
    \beta_4^{(i)} &= (4r_{k,i}^{\prime-1})\hat{y}_{k|k-1}^2 + (-8r_{k,i}^{\prime-1}s_{y,i})\hat{y}_{k|k-1} + (4r_{k,i}^{\prime-1}s_{y,i}^2)\,.

@@

    \State Let $\bm{\alpha}_{v}^{(i)}$ represent the encryption of $\alpha_{v}^{(i)}$ in \eqref{eqn:hrz_linear_comb}
    \State $\bm{\alpha}_{1}^{(i)} \gets \mathcal{E}_{pk_0}(\mathsf{E}_{0}(\hat{x}^3_{k|k-1}))^{\mathsf{E}_{0}(2r_{k,i}^{\prime-1})}\cdot$\par
    \ $\mathcal{E}_{pk_0}(\mathsf{E}_{0}(\hat{x}_{k|k-1}\hat{y}^2_{k|k-1}))^{\mathsf{E}_{0}(2r_{k,i}^{\prime-1})}\cdot$\par
    \ $\mathcal{E}_{pk_0}(\mathsf{E}_{0}(\hat{x}^2_{k|k-1}))^{\mathsf{E}_{0}(-r_{k, i}^{\prime-1}s_{x,i})}\cdot$\par
    \ $\mathcal{E}_{pk_0}(\mathsf{E}_{0}(\hat{y}^2_{k|k-1}))^{\mathsf{E}_{0}(-2r_{k, i}^{\prime-1}s_{x,i})}\cdot$\par
    \ $\mathcal{E}_{pk_0}(\mathsf{E}_{0}(\hat{x}_{k|k-1}))^{\mathsf{E}_{0}(2r_{k,i}^{\prime-1}z_{k,i}')}\cdot$\par
    \ $\mathcal{E}_{pk_0}(\mathsf{E}_{0}(\hat{x}_{k|k-1}))^{\mathsf{E}_{0}(-2r_{k,i}^{\prime-1}s_{x,i}^2)}\cdot$\par
    \ $\mathcal{E}_{pk_0}(\mathsf{E}_{0}(\hat{x}_{k|k-1}))^{\mathsf{E}_{0}(-2r_{k,i}^{\prime-1}s_{y,i}^2)}\cdot$\par
    \ $(N+1)^{\mathsf{E}_{1}(2r_{k,i}^{\prime-1}s_{x,i}^3)}
    (N+1)^{\mathsf{E}_{1}(2r_{k,i}^{\prime-1}s_{x,i}s_{y,i}^2)}\cdot$\par
    \ $(N+1)^{\mathsf{E}_{1}(-2r_{k, i}^{\prime-1}s_{x,i}z_{k,i}')}
    H(k\mathbin\|1\mathbin\|1\mathbin\|0)\pmod{N^2}$
    \State Compute $\bm{\alpha}_{2}^{(i)}$ using \eqref{eqn:hrz_linear_comb}, \eqref{eqn:our_scheme_lin_comb} and the remark from section \ref{sec:lcao_scheme} in the form above
    \For{$v \gets 1$ to $2$}
        \State Send $\bm{\alpha}_{v}^{(i)}$ to the navigator
    \EndFor

    \State Let $\bm{\beta}_{w}^{(i)}$ represent an encryption of $\beta_{w}^{(i)}$ in \eqref{eqn:hrh_linear_comb}
    \State $\bm{\beta}_{1}^{(i)} \gets \mathcal{E}_{pk_0}(\mathsf{E}_{0}(\hat{x}^2_{k|k-1}))^{\mathsf{E}_{0}(4r_{k,i}^{\prime-1})}\cdot$\par
    \ $\mathcal{E}_{pk_0}(\mathsf{E}_{0}(\hat{x}_{k|k-1}))^{\mathsf{E}_{0}(-8r_{k, i}^{\prime-1}s_{x,i})}\cdot$\par
    \ $(N+1)^{\mathsf{E}_{1}(4r_{k,i}^{\prime-1}s_{x,i}^2)}\cdot$\par
    \ $H(k\mathbin\|1\mathbin\|1\mathbin\|1)\pmod{N^2}$
    \State Compute remaining $\bm{\beta}_{w}^{(i)}$ using \eqref{eqn:hrh_linear_comb}, \eqref{eqn:our_scheme_lin_comb} and the remark from section \ref{sec:lcao_scheme} in the form above
    \For{$w \gets 1$ to $4$}
        \State Send $\bm{\beta}_{w}^{(i)}$ to the navigator
    \EndFor
    \EndProcedure
\end{algorithmic}
\end{algorithm}

@@

    \For{$v \gets 1$ to $2$}
        \State Receive $\bm{\alpha}_{v}^{(i)}$ from each sensor $1\leq i \leq n$
    \EndFor

    \For{$w \gets 1$ to $4$}
        \State Receive $\bm{\beta}_{w}^{(i)}$ from each sensor $1\leq i \leq n$
    \EndFor

    \State Let $\bm{\alpha}_{v}$ represent an encryption of $\sum_{i=1}^n\alpha_{v}^{(i)}$
    \For{$v \gets 1$ to $2$}
        \State $\bm{\alpha}_{v} \gets \prod_{i=1}^n\bm{\alpha}_{v}^{(i)}$
        \State Compute $\mathcal{D}_{sk_0}(\bm{\alpha}_{v})$ with $\lambda$ by \eqref{eqn:our_scheme_decrypt}
        \State Compute $\mathsf{E}^{-1}_{1}(\mathcal{D}_{sk_0}(\bm{\alpha}_{v}))$ by \eqref{eqn:decode}
    \EndFor
    \State Construct $\sum_{i=1}^n\vec{i}'_{k,i}$ from decoded decryptions above

    \State Let $\bm{\beta}_{w}$ represent an encryption of $\sum_{i=1}^n\beta_{w}^{(i)}$
    \For{$w \gets 1$ to $4$}
            \State $\bm{\beta}_{w} \gets \prod_{i=1}^n\bm{\beta}_{w}^{(i)}$
            \State Compute $\mathcal{D}_{sk_0}(\bm{\beta}_{w})$ with $\lambda$ by \eqref{eqn:our_scheme_decrypt}
            \State Compute $\mathsf{E}^{-1}_{1}(\mathcal{D}_{sk_0}(\bm{\beta}_{w}))$ by \eqref{eqn:decode}
    \EndFor
    \State Construct $\sum_{i=1}^n\mat{I}'_{k,i}$ from decoded decryptions above
